### 2023-04-08 output/group_1_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.05 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.84 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.29 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.02 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.34 & 0.00 \\
 & no_cause & 0.07 & 0.95 \\
 & non_payment & 0.90 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
 & hasAttyP & 0.61 & 0.00 \\
 & isEntityD & 0.26 & 0.06 \\
 & isEntityP & 0.16 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_1_crimes_50m & 0.00 & 0.06 \\
 & pre_treatment_change_in_group_1_crimes_50m & 0.00 & 0.75 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.22 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.38 & 0.00 \\
 & no_cause & 0.06 & 0.95 \\
 & non_payment & 0.84 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.03 & 0.00 \\
 & hasAttyP & 0.66 & 0.00 \\
 & isEntityD & 0.25 & 0.06 \\
 & isEntityP & 0.19 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_1000m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.18 & 3.58 & 0.18 & 0.65 & 0.80 \\
 & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.49 & -0.01 & 0.93 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.80 & 0.94 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.54 & 0.49 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.63 & 0.52 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_1000m & 59.19 & 3.58 & 0.18 & 0.65 & 0.80 \\
 & pre_treatment_change_in_group_2_crimes_1000m & -0.67 & -0.05 & 0.50 & -0.01 & 0.93 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.60 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 113.70 & 0.94 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 593.73 & 0.49 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.44 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 253.67 & 0.52 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.87 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
 & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.49 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.37 & 0.00 \\
 & no_cause & 0.16 & 0.95 \\
 & non_payment & 0.11 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.66 & 0.00 \\
 & hasAttyP & 0.14 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.54 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_1000m & 0.00 & 0.18 \\
 & pre_treatment_change_in_group_2_crimes_1000m & 0.00 & 0.50 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
 & no_cause & 0.16 & 0.95 \\
 & non_payment & 0.14 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.67 & 0.00 \\
 & hasAttyP & 0.13 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.53 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_100m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 0.96 & 0.08 & 0.64 & -0.00 & 0.99 \\
 & pre_treatment_change_in_group_2_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.64 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 435.35 & 0.52 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.27 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_2_crimes_100m & 0.97 & 0.07 & 0.65 & -0.00 & 0.99 \\
 & pre_treatment_change_in_group_2_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.64 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 436.85 & 0.52 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.27 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.64 \\
 & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.02 & 0.22 \\
 & job_density_2013 & 0.17 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.79 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.43 & 0.00 \\
 & no_cause & 0.29 & 0.95 \\
 & non_payment & 0.80 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.22 & 0.00 \\
 & hasAttyP & 0.45 & 0.00 \\
 & isEntityD & 0.81 & 0.06 \\
 & isEntityP & 0.18 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_100m & 0.00 & 0.65 \\
 & pre_treatment_change_in_group_2_crimes_100m & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.03 & 0.22 \\
 & job_density_2013 & 0.06 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.75 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.30 & 0.00 \\
 & no_cause & 0.28 & 0.95 \\
 & non_payment & 0.97 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.24 & 0.00 \\
 & hasAttyP & 0.43 & 0.00 \\
 & isEntityD & 0.82 & 0.06 \\
 & isEntityP & 0.17 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_50m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_2_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.45 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -42.73 & 0.98 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,914.99 & 0.04 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 688.17 & 0.12 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_2_crimes_50m & 0.24 & 0.07 & 0.01 & -0.01 & 0.44 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.01 & 0.08 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & -31.22 & 0.98 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 1,919.52 & 0.03 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 693.49 & 0.11 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_2_crimes_50m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.03 & 0.01 \\
 & pre_treatment_change_in_group_2_crimes_50m & 0.19 & 0.41 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.98 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
 & no_cause & 0.29 & 0.95 \\
 & non_payment & 0.61 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.30 & 0.00 \\
 & isEntityD & 0.43 & 0.06 \\
 & isEntityP & 0.49 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_2_crimes_50m & 0.02 & 0.01 \\
 & pre_treatment_change_in_group_2_crimes_50m & 0.19 & 0.41 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.01 & 0.05 \\
 & poor_share2010 & 0.98 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.00 \\
 & no_cause & 0.29 & 0.95 \\
 & non_payment & 0.61 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.12 & 0.00 \\
 & hasAttyP & 0.30 & 0.00 \\
 & isEntityD & 0.43 & 0.06 \\
 & isEntityP & 0.49 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_1000m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_1000m & 58.60 & 2.49 & 0.08 & 0.42 & 0.75 \\
 & pre_treatment_change_in_group_3_crimes_1000m & -2.38 & -0.18 & 0.07 & -0.01 & 0.87 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.75 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 64.90 & 0.96 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.64 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 152.34 & 0.68 \\
\cline{1-7}
\textit{Panel C} & no_cause & 0.05 & 0.00 & 0.95 & 0.00 & 0.96 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.01 & 0.06 & 0.00 & 0.92 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_1000m & 415.94 & 15.64 & 0.04 & 0.55 & 0.94 \\
\cline{1-7}
\multirow[c]{5}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.96 \\
 & job_density_2013 & 17,324.75 & 2,509.70 & 0.10 & 19.55 & 0.99 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 64.10 & 0.94 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.00 & 0.94 \\
 & popdensity2010 & 23,285.59 & 1,452.05 & 0.00 & 29.70 & 0.95 \\
\cline{1-7}
\multirow[c]{2}{3cm}{\textit{Panel D}} & hasAttyP & 0.88 & -0.04 & 0.00 & 0.00 & 0.89 \\
 & isEntityP & 0.81 & -0.07 & 0.00 & 0.00 & 0.89 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_1000m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_0_crimes_100m & 0.00 & 0.03 \\
 & pre_treatment_change_in_group_0_crimes_100m & 0.01 & 0.96 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.33 & 0.00 \\
 & no_cause & 0.09 & 0.95 \\
 & non_payment & 0.04 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.62 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_1000m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_3_crimes_1000m & 0.61 & 0.17 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.45 & 0.00 \\
 & no_cause & 0.26 & 0.95 \\
 & non_payment & 0.95 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.99 & 0.00 \\
 & hasAttyP & 0.00 & 0.00 \\
 & isEntityD & 0.15 & 0.06 \\
 & isEntityP & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_100m/tables/balance_table.tex
gennerated figures

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & total_twenty_seventeen_group_3_crimes_100m & 0.95 & 0.07 & 0.67 & 0.00 & 1.00 \\
 & pre_treatment_change_in_group_3_crimes_100m & -0.02 & -0.01 & 0.23 & 0.00 & 0.73 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.01 & 0.22 & 0.00 & 0.63 \\
 & med_hhinc2016 & 48,534.18 & 1,788.07 & 0.05 & 441.33 & 0.52 \\
 & poor_share2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.28 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & total_twenty_seventeen_group_3_crimes_100m & 7.20 & 0.82 & 0.04 & -0.03 & 0.94 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel B}} & frac_coll_plus2010 & 0.33 & 0.02 & 0.09 & -0.01 & 0.52 \\
 & job_density_2013 & 17,324.75 & 6,144.92 & 0.01 & 1,756.80 & 0.47 \\
 & med_hhinc2016 & 48,534.18 & 2,249.48 & 0.13 & -1,615.62 & 0.22 \\
 & popdensity2010 & 23,285.59 & 1,707.93 & 0.03 & -500.51 & 0.47 \\
\cline{1-7}
\textit{Panel D} & isEntityD & 0.02 & -0.04 & 0.00 & -0.02 & 0.01 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_100m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_3_crimes_100m & 0.00 & 0.54 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.72 & 0.09 \\
 & job_density_2013 & 0.00 & 0.01 \\
 & med_hhinc2016 & 0.12 & 0.13 \\
 & poor_share2010 & 0.00 & 0.02 \\
 & popdensity2010 & 0.11 & 0.03 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.71 & 0.50 \\
 & no_cause & 0.14 & 0.00 \\
 & non_payment & 0.69 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.10 & 0.00 \\
 & hasAttyP & 0.15 & 0.00 \\
 & isEntityD & 0.61 & 0.00 \\
 & isEntityP & 0.02 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_100m & 0.00 & 0.04 \\
 & pre_treatment_change_in_group_3_crimes_100m & 0.24 & 0.33 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.09 \\
 & job_density_2013 & 0.02 & 0.01 \\
 & med_hhinc2016 & 0.00 & 0.13 \\
 & poor_share2010 & 0.29 & 0.02 \\
 & popdensity2010 & 0.00 & 0.03 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.19 & 0.50 \\
 & no_cause & 0.42 & 0.00 \\
 & non_payment & 0.08 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.75 & 0.00 \\
 & hasAttyP & 0.31 & 0.00 \\
 & isEntityD & 0.00 & 0.00 \\
 & isEntityP & 0.05 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-08 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
gennerated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.01 \\
 & pre_treatment_change_in_group_3_crimes_500m & 0.00 & 0.55 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.00 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.05 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.18 & 0.00 \\
 & no_cause & 0.27 & 0.95 \\
 & non_payment & 0.07 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.68 & 0.00 \\
 & hasAttyP & 0.42 & 0.00 \\
 & isEntityD & 0.02 & 0.06 \\
 & isEntityP & 0.16 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & total_twenty_seventeen_group_3_crimes_500m & 0.00 & 0.02 \\
 & pre_treatment_change_in_group_3_crimes_500m & 0.04 & 0.81 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & frac_coll_plus2010 & 0.01 & 0.22 \\
 & job_density_2013 & 0.00 & 0.10 \\
 & med_hhinc2016 & 0.00 & 0.05 \\
 & poor_share2010 & 0.00 & 0.96 \\
 & popdensity2010 & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & for_cause & 0.75 & 0.00 \\
 & no_cause & 0.94 & 0.95 \\
 & non_payment & 0.85 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & hasAttyD & 0.43 & 0.00 \\
 & hasAttyP & 0.41 & 0.00 \\
 & isEntityD & 0.00 & 0.06 \\
 & isEntityP & 0.64 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}
